Including EW and mixed QCD-EW corrections into PDF fits

### 2020-04-01 paper/sec-introduction.tex
Intro WIP

The systematic inclusion of EW corrections in a PDF determination entails
the solution of two separate problems. efficiency (produce lookup tables)
and consistency (avoid double counting).
This paper addresses the first problem. How? By developing Pinanppl

@@

>>>>

The systematic inclusion of EW corrections in a PDF determination entails
the solution of two separate problems. First, a problem of efficiency:
fast interpolation grids should be constructed, whereby partonic matrix 
elements, accurate to NLO QCD+EW, are precomputed in such a way that the 
numerical convolution with generic input PDFs can be efficiently approximated
by means of interpolation techniques. Such grids are a fundamental ingredient
in any PDF fit, where the evaluation of the hadronic cross section needs to 
be performed a large number of times. While two default formats exist for
these grids, {\sc APPLgrid}~\cite{Carli:2010rw} and 
{\sc fastNLO}~\cite{Kluge:2006xs}, none of them allows for the inlusion of EW
corrections nor for the interface to a Monte Carlo generator accurate to 
NLO QED+EW. Second, a problem of consistency: the way in which EW effects may
(or may not) be folded into the data varies across different experimental 
analyses, a fact that challenges their consistent theoretical interpretation. 
Examples are the subtraction of background processes which should not be 
considered as such ({\it e.g.} the $t$-channel photon-induced component in 
neutral-current Drell-Yan, which are not different processes beyond LO) or of 
just a part of the EW effects ({\it e.g.} multiple-photon radiation from light 
particles in the final state of neutral- or charged-current Drell-Yan, 
especially with electrons). Be that as it may if EW effects are systematically
included in theoretical predictions, they should not be in the data,
otherwise they will be double counted.

In this paper we address the first of these two problems.
How? By developing {\sc PineAPPL}

the second problem, the solution of which, however, remains beyond the scope of 
the current work.

@@

The paper is organised as follows.
